---
title: "Sampling distributions and the Hartford corrections data"
output:
  html_document: default
  pdf_document: default
---

## Loading data

We got this data from [http://data.hartford.gov/](http://data.hartford.gov/)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
library(mosaic)
library(lubridate)
library(readr)
```




```{r, message=FALSE}
correction <- read_csv("Correctional_Facility_Daily_Population_Count_By_Facility.csv")

correction <- correction %>%
  rename(name = `Facility Name`) %>%
  rename(accused = `Accused/Other Status Count`) %>%
  rename(sentenced = `Sentenced Status Count`) %>%
  rename(total = `Total Facility Population Count`) %>%
  mutate(Date = mdy(Date))
```


## Where are the most accused?

```{r}
correction %>%
  df_stats(accused~name, mean) %>%
  arrange(desc(mean_accused))
```

## Focus on Hartford

```{r}
hartford <- correction %>%
  filter(name == "HARTFORD CC")
```


## Plotting

```{r}
gf_point(accused~Date, data=hartford)
gf_line(accused~Date, data=hartford)
```

## More complicated filtering

I wonder about how Osborn and Enfield look. Let's filter it. 

```{r}
correction %>%
  filter(name == "OSBORN CI" | name == "ENFIELD CI")
```


## Sampling 

(we copied this code from [Danny's resampling lesson](https://dtkaplan.shinyapps.io/Tutorial_resampling/) so we didn't have to start from scratch!)

```{r}
Trials <-   
  do(2000) * {
    correction %>%
      sample_n(size = 50, replace=FALSE) %>%
      df_stats( ~ total, mean)
  }

```

```{r}
gf_histogram(~mean_total, data=Trials)
```

## What if we changed the sample size?

```{r}
Trials5 <- 
  do(2000) * {
    correction %>%
      sample_n(size = 5, replace=FALSE) %>%
      df_stats( ~ total, mean)
  }

Trials10 <- 
  do(2000) * {
    correction %>%
      sample_n(size = 10, replace=FALSE) %>%
      df_stats( ~ total, mean)
  }

Trials100 <- 
  do(2000) * {
    correction %>%
      sample_n(size = 100, replace=FALSE) %>%
      df_stats( ~ total, mean)
  }
```

## (Tidying the data)

```{r}
alltrials <- data.frame(ss5 = Trials5$mean_total, ss10 = Trials10$mean_total, ss100 = Trials100$mean_total)
library(tidyr)
alltrials <- alltrials %>%
  gather(key=which, value=mean)
```

## Plotting the sampling distributions!

```{r}
gf_density(~mean, data=alltrials, fill = ~ which, alpha=.2, position="stack")
gf_jitter(mean ~ which, alpha = 0.1, data = alltrials, width = 0.3) %>% gf_violin(mean~which, data=alltrials, color=NA, fill="blue", alpha=0.4)
df_stats(mean~which, data=alltrials, mean, sd)
```

What about the means of the groups?
 
```{r}
Trials %>%
  df_stats(~mean_total, mean)
```

What was our population mean?
```{r}
correction %>%
  df_stats(~total, mean)
```


