---
title: "Sampling_Distributions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sampling of Data

Have the students in either one class or all statistics class complete a survey using google forms.The survey should involve both quantitative and qualititaive.
Read the data into R. Students then decide if they should take a random sample, statified, systematic, or cluster sample. Then have R take the sample chossen. 

```{r}

```

## Summary statistics

Have students calculate descriptive statitistics on a particular variable.

```{r echo = FALSE}
summary()
```

Students need to type their descriptive statitics into a google sheet. The data in the google sheet could be used in the future to create a sampling distributiuon. 

```{r}
sampling distribution
```

## Confidence interval

Create a confidence interval of a particular variable. Create confidence interval using a different sampling method. 
```{r}

```

## Hyothesis testing

Run a hypothesis test of the variable. Test using different sampling method.

## Compare sample and population
Calculate the mean for the variable from the entire population.
Compare the sample means from the confidence intervals to the population mean.
