---
output: 
  rmarkdown::html_document:
    theme: paper
---
```{r child="../header.md"}
```
<!-- Edit below this line. -->

```{r include = FALSE}
library(SDSdata)
library(htmltools)
```

<!--0 “default”, “cerulean”, “journal”, “flatly”, “readable”, “spacelab”, “united”, “cosmo”, “lumen”, “paper”, “sandstone”, “simplex”, “yeti” -->

<!-- Make the thumbnails with `make_thumbnail_image()` in SDSdata, e.g.
make_thumbnail_image("https://dtkaplan.shinyapps.io/Starbucks/#section-visualizing-starbucks-locations", delay = 10)
-->

# StatPREP lessons and tutorials

A StatPREP **tutorial** is an interactive document mainly intended to help **instructors** develop statistical, graphical, and general computing skills using R statements. In contrast, a StatPREP **lesson** is intended for use with students, for instance as an in-class demonstration or activity. 

This page provides links to lessons based on interacting with R. Each link takes you to a web service that displays the document in your web browser. You don't need to install any other software on your computer to use the lessons and tutorials.

In the following, **lessons** are intended for use in class or other student-oriented settings. In contrast, **tutorials** are intended to help instructors (or others) develop general skills in using MOSAIC for statistical and graphical calculations.



```{r echo = FALSE}
# make_thumbnail_image("https://dtkaplan.shinyapps.io/Functions/", delay = 10)
functions_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Functions/",
                                 "thumbnails/functions.png",
                                 "Functions in R")
# make_thumbnail_image("https://dtkaplan.shinyapps.io/Formulas/", delay = 10)
formulas_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Formulas/",
                                 "thumbnails/formulas.png",
                                 "Formulas")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Data_frames/", delay = 10)
data_frames_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_data_frames/",
                                 "thumbnails/tutorial_data_frames.png",
                                 "Data frames")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Counting/", delay = 10)
counting_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_Counting/",
                                "thumbnails/tutorial_counting.png", 
                                "Counts and proportions")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Calculating_statistics/")
dfstats_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_Calculating_statistics/",
                               "thumbnails/tutorial_calculating_statistics.png",
                               "Calculating statistics")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Densities/")
densities_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_Densities/",
                               "thumbnails/tutorial_densities.png",
                               "Histograms and better")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/tutorial_conventional_graphics/#section-histogram")
conventional_graphics_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/tutorial_conventional_graphics/",
                               "thumbnails/tutorial_conventional.png",
                               "Conventional graphics")


# make_thumbnail_image("https://dtkaplan.shinyapps.io/tutorial_data_science_graphics/#section-graphics-for-descriptive-statistics")
data_graphics_thumb <- app_thumbnail(
  "https://dtkaplan.shinyapps.io/tutorial_data_science_graphics/", 
  "thumbnails/tutorial_data_graphics.png",
  "Data science graphics")

# make_thumbnail_image("http://dtkaplan.shinyapps.io/Five_data_verbs")
data_verbs_thumb <- app_thumbnail("http://dtkaplan.shinyapps.io/Five_data_verbs", 
                 "thumbnails/five_data_verbs.png",
                 "Five data verbs✐")

# make_thumbnail_image("http://dtkaplan.shinyapps.io/Workshop_wrangling")
workshop_wrangling_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Workshop_wrangling", 
                "thumbnails/workshop_wrangling.png",
                "Data wrangling✐")

# make_thumbnail_image("http://dtkaplan.shinyapps.io/Tutorial_regression")
regression_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Tutorial_regression", 
                "thumbnails/Tutorial_regression.png",
                "Regression")

# make_thumbnail_image("http://dtkaplan.shinyapps.io/Tutorial_classical_inference")
classical_inference_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Tutorial_classical_inference", 
                "thumbnails/Tutorial_classical_inference.png",
                "Classical statistical inference")

# make_thumbnail_image("http://dtkaplan.shinyapps.io/Tutorial_its_all_regression")
its_all_regression_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Tutorial_its_all_regression", 
                "thumbnails/Tutorial_its_all_regression.png",
                "Streamlining inference with regression")


# make_thumbnail_image("http://dtkaplan.shinyapps.io/Tutorial_resampling")
resampling_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Tutorial_resampling", 
                "thumbnails/Tutorial_resampling.png",
                "Resampling")

# make_thumbnail_image("http://dtkaplan.shinyapps.io/Tutorial_sampling")
sampling_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Tutorial_sampling", 
                "thumbnails/Tutorial_sampling.png",
                "Sampling")

```

## Tutorials

### R and data fundamentals
```{r echo = FALSE}
div(class = "row",
    functions_thumb, formulas_thumb, data_frames_thumb)
```
    
### Descriptive statistics & graphics
```{r echo = FALSE}    
div(class = "row", 
     counting_thumb, dfstats_thumb, densities_thumb,
     conventional_graphics_thumb, data_graphics_thumb)
```

### Data wrangling

```{r echo = FALSE}    
div(class = "row", data_verbs_thumb, workshop_wrangling_thumb)
```

### Inference and regression

```{r echo = FALSE}    
div(class = "row", 
    regression_thumb, classical_inference_thumb, its_all_regression_thumb,
    sampling_thumb, resampling_thumb
)
```


## Lessons




```{r echo = FALSE}
# make_thumbnail_image("https://dtkaplan.shinyapps.io/Lesson_first_day_births/", delay = 10)
first_day_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Lesson_first_day_births/",
                                 "thumbnails/lesson_first_day_births.png",
                                 "A first-day lesson")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Globe_toss/")
globe_toss_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/tutorial_globe_toss.png", 
                "thumbnails/tutorial_globe_toss.png",
                "Collecting data: Globe toss✐")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Riverboat_shuffle/")
riverboat_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Tutorial_Riverboat_shuffle.png", 
                "thumbnails/tutorial_riverboat_shuffle.png",
                "A Riverboat Card Trick✐")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Lesson_read_class_data/")
read_class_data_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Lesson_read_class_data.png", 
                "thumbnails/lesson_read_class_data.png",
                "Accessing in-class data")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Whats_normal/#section-the-age-distribution-graphically")
whats_normal_thumb <- 
  app_thumbnail("http://dtkaplan.shinyapps.io/Whats_normal", 
                "thumbnails/whats_normal.png",
                "What's normal?")

```

```{r echo = FALSE}
div(class = "row",
    first_day_thumb, globe_toss_thumb, riverboat_thumb, read_class_data_thumb, whats_normal_thumb
)
```







