---
output: 
  rmarkdown::html_document:
    theme: paper
---
```{r child="../header.md"}
```
<!-- Edit below this line. -->

```{r include = FALSE}
library(SDSdata)
library(htmltools)
```

“default”, “cerulean”, “journal”, “flatly”, “readable”, “spacelab”, “united”, “cosmo”, “lumen”, “paper”, “sandstone”, “simplex”, “yeti”

<!-- Make the thumbnails with `make_thumbnail_image()` in SDSdata, e.g.
make_thumbnail_image("https://dtkaplan.shinyapps.io/Starbucks/#section-visualizing-starbucks-locations", delay = 10)
-->

# StatPREP R

This page provides links to lessons based on interacting with R. Each link takes you to a web service that displays the document in your web browser. You don't need to install any other software on your computer to use the lessons and tutorials.

The StatPREP approach to statistics uses the R notation developed by Project MOSAIC, based on a simple, consistent template that works across statistical operations and graphics.

In the following, **lessons** are intended for use in class or other student-oriented settings. In contrast, **tutorials** are intended to help instructors (or others) develop general skills in using MOSAIC for statistical and graphical calculations.

## Tutorials

```{r echo = FALSE}
# make_thumbnail_image("https://dtkaplan.shinyapps.io/Functions/", delay = 10)
functions_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Functions/",
                                 "thumbnails/functions.png",
                                 "Functions in R")
# make_thumbnail_image("https://dtkaplan.shinyapps.io/Formulas/", delay = 10)
formulas_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Formulas/",
                                 "thumbnails/formulas.png",
                                 "Formulas")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Data_frames/", delay = 10)
data_frames_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_data_frames/",
                                 "thumbnails/tutorial_data_frames.png",
                                 "Data frames")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Counting/", delay = 10)
counting_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_Counting/",
                                "thumbnails/tutorial_counting.png", 
                                "Counts and proportions")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Calculating_statistics/")
dfstats_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_Calculating_statistics/",
                               "thumbnails/tutorial_calculating_statistics.png",
                               "Calculating statistics")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Tutorial_Densities/")
densities_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Tutorial_Densities/",
                               "thumbnails/tutorial_densities.png",
                               "Histograms and better")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/tutorial_conventional_graphics/#section-histogram")
conventional_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/tutorial_conventional_graphics/",
                               "thumbnails/tutorial_conventional.png",
                               "Conventional graphics")


```

```{r echo = FALSE}
div(class = "row",
    functions_thumb, formulas_thumb, data_frames_thumb, counting_thumb, dfstats_thumb, densities_thumb, conventional_thumb
)
```


## Lessons




```{r echo = FALSE}
# make_thumbnail_image("https://dtkaplan.shinyapps.io/Lesson_first_day_births/", delay = 10)
first_day_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/Lesson_first_day_births/",
                                 "thumbnails/lesson_first_day_births.png",
                                 "A first-day lesson")
```

```{r echo = FALSE}
div(class = "row",
    first_day_thumb, first_day_thumb
)
```







