---
title: "Los Angeles Local Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(ggformula)
library(mosaic)
library(mosaicCore)
```

## Active Businesses

```{r eval =  FALSE}
Businesses <- read_csv("Raw_data/Listing_of_Active_Businesses.csv")



Businesses <- 
  Businesses %>%
  select(zip = "ZIP CODE", naics_code = NAICS, naics = "PRIMARY NAICS DESCRIPTION",
         start = "LOCATION START DATE") %>%
  mutate(start = lubridate::mdy(start))

save(Businesses, file = "Data/Businesses.rda")
today <- lubridate::mdy("6/21/2018")
Businesses <- Businesses %>% 
  mutate(duration = interval(start, today) %>% as.numeric("months"))
```

```{r warning = FALSE}
load("Data/Businesses.rda")


# Get description levels
NAICS <- Businesses %>%
  group_by(naics_code, naics) %>%
  summarize(count = n()) %>%
  mutate(code = as.character(naics_code))

Majors <- 
  Businesses %>%
  left_join(NAICS) %>%
  filter(count > 4000)

gf_violin(duration ~ code, data = Majors) %>%
  gf_theme(axis.text.x = element_text(angle = 45, hjust = 1)) %>%
  gf_labs(x = "NAICS code", y = "Months in business")
```


## Arrests

[Data source](https://data.lacity.org/A-Safe-City/Arrest-Data-from-2010-to-Present/yru6-6re4)

```{r eval = FALSE}
Arrests <- read_csv("Raw_data/Arrest_Data_from_2010_to_Present.csv")
Arrests <- Arrests %>%
  select(date = "Arrest Date", time = Time, age = Age, sex = "Sex Code",
         descent = "Descent Code",
         charge_gp_code = "Charge Group Code",
         charge_gp = "Charge Group Description",
         arrest = "Arrest Type Code",
         charge = Charge,
         location = Location
         )
save(Arrests, file = "Data/Arrests.rda")
```


```{r}
load("Data/Arrests.rda")
```

```{r}
Arrests %>%
  group_by(charge_gp) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

A code to indicate the type of charge the individual was arrested for. 

- D - Dependent 
- F - Felony 
- I - Infraction 
- M - Misdemeanor 
- O - Other

```{r}
Arrests %>%
  group_by(arrest) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

Descent Code: 

- A - Other Asian 
- B - Black 
- C - Chinese 
- D - Cambodian 
- F - Filipino 
- G - Guamanian 
- H - Hispanic/Latin/Mexican 
- I - American Indian/Alaskan Native 
- J - Japanese 
- K - Korean
- L - Laotian 
- O - Other 
- P - Pacific Islander 
- S - Samoan 
- U - Hawaiian 
- V - Vietnamese 
- W - White 
- X - Unknown 
- Z - Asian Indian

```{r}
Arrests %>%
  group_by(descent) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

```{r}
Arrests <-
  Arrests %>%
  mutate(group = ifelse(descent %in% c("H", "B", "W"), descent, "O"))
gf_counts( ~ group, fill = ~ arrest, data = Arrests, position = "fill")
```

