---
title: "St Paul Parks and Rec"
author: "Stat PREP 2018"
date: "6/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(mosaic)
options(digits = 3)
```

## Data Sources

### Parks and Rec Survey

The Parks and Rec Survey was administered in 2016 to subscribers to the Parks and Recreation electronic new bulletin.  Find out more at [https://information.stpaul.gov](https://information.stpaul.gov/Public-Facilities-Services/Parks-And-Recreation-Community-Interest-Survey-Dat/x757-9f5s).

> An online survey was sent to Parks and Recreation e-delivered news bulletin subscribers. The 
subscriber lists for two Parks and Recreation e-lists – 'Parks and Recreation Updates' and the 
'Parks and Recreation News, Events and Activities' – were used.  The first survey mailing was 
sent to these subscribers on August 17th.  Reminders were sent on August 26th and September 2, 
2016, and the survey was closed on September 9, 2016. The result was a 17% "opened" rate for 
these emails, which means that 4,762 surveys were successfully delivered. Of these, 1,382 
responses were received for a 29% response rate.

### Zip Codes

Zip code geography data (location information) is from [https://simplemaps.com/data/us-zips](https://simplemaps.com/data/us-zips).

Zip Code Demography data is from Danny Kaplan (personal communication).

## Loading the Data

```{r}
library(readr)
ParksRec <- 
  read_csv("Parks_And_Recreation_Community_Interest_Survey_Dataset.csv")
load('ZipDemography.rda')  # load ZipDemography
ZipGEO <- read_csv("USzips.csv")
```

```{r}
require(dplyr)
ParksRecPlus <-
  ParksRec %>%
  left_join(ZipDemography, by = c(zip = "ZIP")) %>%
  left_join(ZipGEO) %>%
  mutate(
    zip = readr::parse_number(zip),
    RegionalParkUse = 
      factor(RegionalParkUse, 
             levels=c("I/we don't use this", "A few times a year", 
                      "A few times a month", "A few times a week", 
                      "Almost daily")),
    RegionalParksCondition = 
      factor(RegionalParksCondition,
             levels = c("Excellent", "Good", "Fair", 
                        "Poor", "I/we don't use this")
      )
    )
```

## Plotting the Data

```{r}
gf_jitter( RegionalParksCondition ~ MedianAge, data = ParksRecPlus, alpha = 0.15)
```
## Looking at the "young" zip codes

```{r}
ParksRecPlus %>% 
  filter(MedianAge < 25) %>%
  select(zip, MedianAge, RegionalParksCondition, county_name, lat, lng)
```

## Merging the summary data

```{r}
ParksRecByZip <-
  ParksRecPlus %>%
  group_by(zip, MedianAge, lat, lng, county_name) %>%
  summarise(n = n()) %>%
  left_join(
    df_stats(RegionalParksCondition ~ zip, data = ParksRecPlus, n = length, props)
  )

```

## Presenting data on a map

```{r}
require(leaflet)
leaflet(data = ParksRecByZip) %>% addTiles() %>%
  addMarkers(~lng, ~lat,
             popup = ~ as.character(county_name), 
             label = ~ paste(
               "Zip = ", as.character(zip), 
               "; Med. Age = ", as.character(MedianAge), 
               "; Prop. Excellent = ", round(prop_Excellent, 2),
               "; Prop. Good = ", round(prop_Good, 2),
               "; n = ", n))
 
```

