---
title: "Numerical Summaries in R"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(NHANES)
library(mosaic)
```


## Computing Means using df_stats()

Let's learn how to get R to compute **means** from our data.



### Example

Here is our first example.  Notice how it uses our 
formula template (just like `ggformula`).


```{r mean-example, exercise=TRUE}
gf_jitter(Age ~ Gender, data = NHANES, alpha = 0.04)
 df_stats(Age ~ Gender, data = NHANES, mean)
```

#### Your Turn

Change the variable `Age` to some other variable.  Examples: `Weight`, `Length`,
`HeadCirc`, `BMI`, etc.  (Use `?NHANES` to get a full list of variables.)

```{r mean-exercise, exercise=TRUE}
gf_jitter( ??? ~ Gender, data = NHANES, alpha = 0.04)
 df_stats( ??? ~ Gender, data = NHANES, mean)
```

## Why stop at means?

Try replacing mean with some other statistical summaries, for example, let's try **median**.

```{r dfstats-median, exercise=TRUE, exercise.eval=TRUE}
df_stats( Age ~ Gender, data = NHANES, median)
```

#### Your Turn

1. Try some other statistics: `sd`, `max`, `min`, `range`, `iqr`.

```{r dfstats-median-exercise, exercise=TRUE}
df_stats( Age ~ Gender, data = NHANES, ???)
```


```{r dfstats-median-exercise-hint}
df_stats( Age ~ Gender, data = NHANES, sd)
```


2. What happens if you try more than one summary at the same time? Try it.

```{r dfstats-meansd, exercise=TRUE}
df_stats( Age ~ Gender, data = NHANES, mean, sd, range)
```

3. What if you don't use any?  Try it.

```{r dfstats-favstats, exercise=TRUE}
df_stats( Age ~ Gender, data = NHANES)
```
