---
output: 
  rmarkdown::html_document:
    theme: paper
---
```{r child="../header.md"}
```
<!-- Edit below this line. -->

```{r include = FALSE}
library(SDSdata)
library(htmltools)
```

<!--0 “default”, “cerulean”, “journal”, “flatly”, “readable”, “spacelab”, “united”, “cosmo”, “lumen”, “paper”, “sandstone”, “simplex”, “yeti” -->

<!-- Make the thumbnails with `make_thumbnail_image()` in SDSdata, e.g.
make_thumbnail_image("https://dtkaplan.shinyapps.io/Starbucks/#section-visualizing-starbucks-locations", delay = 10)
-->

# StatPREP Little Apps

StatPREP Little Apps are designed to let students explore specific statistical techniques in the context of data. 




```{r echo = FALSE}

t2_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/LittleApp-t2/",
                                 "thumbnails/LittleApp-t2.png",
                                 "Two-sample t")

smoother_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/LittleApp_smoothing/",
                                 "thumbnails/LittleApp-smoother.png",
                                 "Regression and Smoothers")

proportion_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/LittleApp_proportions/",
                                 "thumbnails/littleapp-proportion.png",
                                 "Proportions")

center_spread_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-why-density/",
                                 "thumbnails/littleapp-center-and-spread.png",
                                 "Center and Spread")

why_density_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/LittleApp_center-and-spread/",
                                 "thumbnails/littleapp-center-and-spread.png",
                                 "Why density and not count?")

# make_thumbnail_image("https://dtkaplan.shinyapps.io/Formulas/", delay = 10)
# make_thumbnail_image("https://dtkaplan.shinyapps.io/littleapp-density-graphs/", delay = 10)
# make_thumbnail_image("https://dtkaplan.shinyapps.io/littleapp-stem-and-leaf/", delay = 10)
# make_thumbnail_image("https://dtkaplan.shinyapps.io/littleapp-generate-resamples/", delay = 10)
# make_thumbnail_image("https://dtkaplan.shinyapps.io/littleapp-ANOVA-1/", delay = 10)
# make_thumbnail_image("https://dtkaplan.shinyapps.io/littleapp-why-density/", delay = 60)
```

```{r echo = FALSE}
div(class = "row",
    t2_thumb, smoother_thumb, proportion_thumb, center_spread_thumb)
```
 
 
## Original style

Feedback on the original Little Apps has prompted us to revise them, adding features such as tabs for the codebook, an explanation, and R code in the app itself. The following Little Apps have not yet been revised, but will be this summer. Still, the main ideas are present in the original version.

```{r echo = FALSE}
Resampling_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-generate-resamples/",
                                 "thumbnails/littleapp-generate-resamples.png",
                                 "Resampling & inference")
ANOVA1_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-anova-1/",
                                 "thumbnails/littleapp-anova-1.png",
                                 "'One-way' ANOVA")
Density_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-density-graphs/",
                                 "thumbnails/littleapp-density-graphs.png",
                                 "Displays of density")
Stem_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-stem-and-leaf/",
                                 "thumbnails/littleapp-stem-and-leaf.png",
                                 "Stem-and-leaf plots")
Why_density_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-why-density/",
                                   "thumbnails/why-density-data-graphics.png",
                                   "Why density and not count?")
Why_density2_thumb <- app_thumbnail("https://dtkaplan.shinyapps.io/littleapp-why-density/",
                                   "thumbnails/why-density-conventional.png",
                                   "Why density and not count?")


```

```{r echo = FALSE}
div(class = "row",
    Resampling_thumb, ANOVA1_thumb, Why_density_thumb)
``` 

### Little Apps for some conventional graphics.

These apps **don't** use the "data graphics/statistical graphics/inference graphics" tricotomy. Instead, they use the varied and inconsistent forms of traditional graphics.

```{r echo = FALSE}
div(class = "row",
    Density_thumb, Stem_thumb, Why_density2_thumb)
``` 

## Instructor orientation

These are documents describing some of the ways the Little Apps can be used.

* [Two-sample t test app](http://gifted-saha-3345d3.netlify.com//post/little-apps-two-sample-t-test/)
* [Smoothing and covariates app](http://gifted-saha-3345d3.netlify.com//post/smoothing-and-covariates)
* [Resampling and confidence app](/http://gifted-saha-3345d3.netlify.com/post/little-apps-resampling-and-confidence)
* [ANOVA in one variable app](http://gifted-saha-3345d3.netlify.com/post/little-apps-anova-in-one-variable/)   
* [Center and spread app](http://gifted-saha-3345d3.netlify.com//post/little-apps-center-and-spread)
* [Why density instead of counts? app](http://gifted-saha-3345d3.netlify.com//post/little-apps-why-use-density/).
* [Proportions app](http://gifted-saha-3345d3.netlify.com//post/proportions-and-zero-one-variables/)
* [Displaying distributions app](/http://gifted-saha-3345d3.netlify.com/post/displaying-distributions/)
* [Stem-and-leaf app](http://gifted-saha-3345d3.netlify.com/post/little-apps-stem-and-leaf-displays)
* [Why density instead of counts? app](http://gifted-saha-3345d3.netlify.com/post/little-apps-why-use-density/). 

